Clustering analysis and statistics

### 2019-08-20 notebooks/Clustering analysis.Rmd

clean_trees <- lapply(clean_trees,
                      function(x) {
                        x@data$Bootstrap <- factor(
                          case_when(
                            x@data$UFboot >= 95 ~ "> 95",
                            x@data$UFboot < 95 &
                              x@data$UFboot >= 80 ~ "80 - 94",
                            x@data$UFboot < 80 &
                              x@data$UFboot >= 50 ~ "50 - 79",
                            x@data$UFboot < 50 ~ "< 50"
                          ),
                          ordered = TRUE,
                          levels = c("> 95",
                                     "80 - 94",
                                     "50 - 79",
                                     "< 50")
                        )
                        return(x)
                      })

@@

boot_palette <- c("> 95" = "#6a51a3",
              "80 - 94" = "#9e9ac8",
              "50 - 79" = "#cbc9e2",
              "< 50" = "#f2f0f7")

>>>>

clean_trees <- lapply(clean_trees,
                      function(x) {
                        x@data$Bootstrap <- factor(
                          case_when(
                            x@data$UFboot >= 95 ~ ">= 95",
                            x@data$UFboot < 95 &
                              x@data$UFboot >= 80 ~ "80 - 94",
                            x@data$UFboot < 80 &
                              x@data$UFboot >= 50 ~ "50 - 79",
                            x@data$UFboot < 50 ~ "< 50"
                          ),
                          ordered = TRUE,
                          levels = c(">= 95",
                                     "80 - 94",
                                     "50 - 79",
                                     "< 50")
                        )
                        return(x)
                      })

@@

boot_palette <- c(">= 95" = "#6a51a3",
              "80 - 94" = "#9e9ac8",
              "50 - 79" = "#cbc9e2",
              "< 50" = "#f2f0f7")
